---
title: "Work Sheet 6"
author: "Neil Francis N. Navarro"
date: "2022-11-24"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***Use the dataset mpg***

```{r, one}
library(ggplot2)
data(mpg)
as.data.frame(data(mpg))
```

**data(mpg)**

```{r, data1}
data("mpg")
str("mpg")
library(dplyr)
glimpse(mpg)
```



***Example. graph using ggplot()***

**ggplot(mpg, aes(cty, hwy)) +
  geom_point()**

***1. How many columns are in mpg dataset? How about the number of rows? Show the codes and its result.***
*Answer= There are 11 columns and 234 rows in the mpg data frame.*

```{r, num1}
nrow(mpg)

ncol(mpg)
```


***2. Which manufacturer has the most models in this data set? Which model has the most variations?***
*Answer= dodge has 37 models*

**a. Group the manufacturers and find the unique models. Copy the codes and result.**

```{r, numb2a}
datampg <- mpg
num2a <- datampg %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
num2a

colnames(num2a) <- c("Manufacturer", "Model","Counts")
num2a
```

**b. Graph the result by using plot() and ggplot(). Write the codes and its result.**

+
**plot**
```{r, numb2b1}
qplot(model, data = mpg,geom = "bar", fill=manufacturer)
```

+
**ggplot**
```{r, numb2b2}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

**3. Same dataset will be used. You are going to show the relationship of the model and the manufacturer.**

```{r, numb3}
datampg <- mpg
num3 <- datampg %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
num3

colnames(num3) <- c("Manufacturer", "Model")
num3
```

***a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?***

```{r, numb3a}
ggplot(mpg, aes(model, manufacturer)) + geom_point()
```

*Answer= geometric point graph of mpg(model and manufacturer)*

***b. For you, is it useful? If not, how could you modify the data to make it more informative? ***

*Answer= Yes, It is useful because you could trackdown the data of each model of the manufacturer*

+
**to modify the data:**

```{r, numb3b}
ggplot(mpg, aes(model, manufacturer)) + 
  geom_point() +
  geom_jitter()
```

***4. Using the pipe (%>%), group the model and get the number of cars per model.Show codes and its result.***

```{r, numb4}
datampg4 <- num2a %>% group_by(Model) %>% count()
datampg4

colnames(datampg4) <- c("Model","Counts")
```

**a. Plot using the geom_bar() + coord_flip() just like what is shown below. Show codes and its result**

```{r, numb4a}
qplot(model,
      data = mpg,main = "Number of Cars per Model", 
      xlab = "Model",
      ylab = "Number of Cars", 
      geom = "bar", fill = manufacturer
      + coord_flip())
```

**b. Use only the top 20 observations. Show code and results.**

```{r, numb4b}
barplot(datampg4$Counts[1:20],
        names.arg=datampg4$Model[1:20])
```

***5. Plot the relationship between cyl - number of cylinders and displ - engine displacement using geom_point with aesthetic colour = engine displacement.Title should be “Relationship  between No. of Cylinders and Engine Displacement”.***

**a. Show the codes and its result.**

```{r, numb5a}
ggplot(data = mpg , mapping = aes(x = displ, y = cyl, 
      main = "Relationship between No of Cylinders and Engine Displacement")) + 
  geom_point(mapping=aes(colour = "engine displacement")) + geom_jitter()
```

**b. How would you describe its relationship?**

*Anwer= So according to the data by the making cyl into y, the graph is jittered. And the pink color indicates the engine displacement as what can you see it is in a dots on a straight horizontal position.*

***6.Get the total number of observations for drv - type of drive train (f = front-wheel drive,r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 2seater, etc.) Plot using the geom_tile() where the number of observations for class be used as a fill for aesthetics.***

**a. Show the codes and its result for the narrative in 6.**

```{r, numb6a}
ggplot(data = mpg, mapping = aes(x = drv, y = class)) + 
  geom_point(mapping=aes(color=class)) +
  geom_tile()
```

**b. Interpret the result: **

*Answer= Areas covered with black are "mapped" using the mapping geometric point graph. y as class and x as drv.*

***7. Discuss the difference between these codes. Its outputs for each are shown below.***

+
**Code 1**

```{r, numb7.1}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy, colour = "blue"))
```

+
**+ Code 2**

```{r, numb7.2}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy), colour = "blue")
```

***8. Try to run the command ?mpg. What is the result of this command?***

```{r, numb8}
?mpg
```
**Answer= It would search mpg data and it will open the r documentation that shows the description of the "mpg" data frame.**

**a. Which variables from mpg dataset are categorical? **

*Answer= Categorical variables in mpg which include: the manufacturer, model, trans (type of transmission), drv (front-wheel drive, rear-wheel, 4wd), fl (fuel type), and class (type of car).*

**b. Which are continuous variables?**
*Answer= Continuous varibles in R was also known as doubles or integers. *

**c. Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon). Mapped it with a continuous variable you have identified in 5-b.**

```{r, numb8c}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()
```

**What is its result? Why it produced such output? **
*Answer= data tracks the cty by placing cty(city miles per gallon) at color having a variation or hues of blue.*

***9.Plot the relationship between displ (engine displacement) and hwy(highway miles per gallon) using geom_point(). Add a trend line over the existing plot using geom_smooth() with se = FALSE. Default method is “loess”.***

```{r, numb9}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
```

***10.Using the relationship of displ and hwy, add a trend line over existing plot. Set the se = FALSE to remove the confidence interval and method = lm to check for linear modeling***

```{r message=FALSE, warning=FALSE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE)
```
