---
title: "Work Sheet 4"
author: "Neil Francis N. Navarro"
date: "2022-11-20"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***1. The table below shows the data about shoe size and height. Create a data frame..***

**library(dplyr)**
**library(readr)**
**library(data.table)**


**a. Describe the data.**

```{r, num1a}
Shoesize <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,
              7.5,10.5,8.5,12.0,10.5,
              13.0,11.5,8.5,5.0,10.0,
              6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)

Height <- c(66.0,68.0,64.5,65.0,70.0,
            64.0,70.0,71.0,72.0,64.0,
            74.5,67.0,71.0,71.0,77.0,72.0,
            59.0,62.0,72.0,66.0,64.0,67.0,73.0,
            69.0,72.0,70.0,69.0,70)

Gender <- c("F","F","F","F","M","F","M","F","M",
             "M","M","F","M","M","M","M","F","F",
            "M","F","M","M","M","F","M","M","M","M")

 data_frame <- data.frame(Shoesize,Height,Gender)
 data_frame
```
 
***Answer: The output will show a data base on what we put on each rows within the dataframe***
 
**b. Find the mean of shoe size and height of the respondents.**
**Copy the codes and results.**

+
***Male***

```{r, male}
Boy <- subset(data_frame, Gender == "M")
mean(Boy$Shoesize)
mean(Boy$Height)
```

+
***Female***

```{r, female}
Girl <- subset(data_frame, Gender == "F")
mean(Girl$Shoesize)
mean(Girl$Height)
```

**c. Is there a relationship between shoe size and height? Why?**

**Yes, The Higher the value of height, the greater value of the Shoesize.**
**and the factor levels below are the actual values.**

***2. Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.***

```{r, num2}
Months_Vector <- c("March","April","January","November","January",
            "September","October","September","November","August",
            "January","November","November","February","May","August",
            "July","December","August","August","September","November","February","April")
Factor_Month_Vector <- factor(Months_Vector)
Factor_Month_Vector
```

***3. Then check the summary() of the Months_Vector_vector and Factor_Month_Vector_vector.***
**Interpret the results of both vectors. Are they both equally useful in this case?**

```{num3}
summary(Months_Vector)
summary(Factor_Month_Vector)
```

**Answer: For me Yes, as for the months_vector it shows the number of months and its class and mode, while the factor_Month_Vector the month has been factor by level and alphabetical and it show the number of each months.**


***4. Create a vector and factor for the table below.***

```{r, num4}
factorData <- data.frame(
 Direction = c("East","West","North"),
 Frequency = c(1,4,3)
)
factorData

newOrderData <- factor(factorData,levels = c("East","West","North"))
print(newOrderData)
```

***5. Enter the data below in Excel with file name = import_march.csv***

**a. Import the excel file into the Environment Pane using read.table() function.**

```{r, num5a}
library(readr)
import_march <- read.table("import.march.csv")
View(import_march)
```

**b. View the dataset. Write the code and its result.**

```{r, num5b}
import_march)
```

***Result***

# A tibble: 101 × 12

   ...1  ...2              ...3             ...4            ...5  ...6  ...7   ...8 ...9  ...10 ...11 ...12
   
   
   <lgl> <chr>             <chr>            <chr>           <chr> <chr> <lgl> <dbl> <chr> <chr> <dbl> <dbl>
   
   
 1 NA    Sepal Length (cm) Sepal Width (cm) Petal Length (… Peta… Class NA       NA alpha obj      NA    NA
 
 2 NA    7                 3.2              4.7             1.4   Iris… NA        0 0     0         0     1
 
 3 NA    6.4               3.2              4.5             1.5   Iris… NA        0 NA    NA        0     1
 
 4 NA    6.9               3.1              4.9             1.5   Iris… NA        0 NA    NA        0     1
 
 5 NA    5.5               2.3              4               1.3   Iris… NA        0 NA    NA        0     1
 
 6 NA    6.5               2.8              4.6             1.5   Iris… NA       NA NA    NA        0     1
 
 7 NA    5.7               2.8              4.5             1.3   Iris… NA       NA NA    NA        0     1
 
 8 NA    6.3               3.3              4.7             1.6   Iris… NA       NA NA    NA        0     1
 
 9 NA    4.9               2.4              3.3             1     Iris… NA       NA NA    NA        0     1
 
10 NA    6.6               2.9              4.6             1.3   Iris… NA       NA NA    NA        0     1

