---
title: "Work Sheet 7"
author: "Neil Francis N. Navarro"
date: "`r Sys.Date()`"
output: word_document
---

***1. Create a data frame for the table below***

```{r,}
Student <- seq(1:10)
PreTest <- c(55,54,47,57,51,61,57,54,63,58)
PostTest <- c(61,60,56,63,56,63,59,56,62,61)

num1 <- data.frame(Student,PreTest,PostTest)
num1
```


***a. Compute the descriptive statistics using different packages (Hmisc and pastecs).***

**Write the codes and its result.**

```{r,}
library(Hmisc)
library(pastecs)
```

```{r,}
describe(num1)
```

```{r,}
stat.desc(num1)
```


***2. The Department of Agriculture was studying the effects of several levels of fertilizer on the growth of a plant. For some analyses, it might be useful to convert the fertilizer levels to an ordered factor.***

**• The data were 10,10,10, 20,20,50,10,20,10,50,20,50,20,10.**

```{r,}
num2 <- c(10,10,10,20,20,50,10,
          20,10,50,20,50,20,10)
num2
```


***a. Write the codes and describe the result.***

```{r,}
num2factor <- factor(num2, ordered = TRUE)
num2factor
```


***3. Abdul Hassan, president of Floor Coverings Unlimited, has asked you to study the exercise levels undertaken by 10 num3 were “l”, “n”, “n”, “i”, “l” , “l”, “n”, “n”, “i”, “l” ; n=none, l=light, i=intense***


```{r,}
num3 <- c("l","n","n","i","l","l","n","n","i","l")
```


**a. What is the best way to represent this in R?**

*Factor*

```{r,}
factor(num3, levels = c("n","l","i"))
```


***4.Sample of 30 tax accountants from all the states and territories of Australia and their individual state of origin is specified by a character vector of state mnemonics as:***


```{r,}
state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld",
           "vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
           "wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
           "vic", "vic", "act")

```

**a. Apply the factor function and factor level. Describe the results.**

*factor function and factor level*

```{r,}
num4a <- factor(state)
num4a
```

**The result shows the levels of the states of the given data.**

*Getting factor level of states*

***5. From #4 - continuation:***

**Suppose we have the incomes of the same tax accountants in another vector (in suitably large units of money)**

```{r,}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)
```


**a. Calculate the sample mean income for each state we can now use the special function tapply():***

```{r,}
num5a <- tapply(incomes, state, mean)
num5a
```


**b. Copy the results and interpret.**

```{r,}
num5a
```

*The result show the level and means of the income of each states.*


***6.Calculate the standard errors of the state income means (refer again to number 3)***



**a. What is the standard error? Write the codes.**

```{r,}
num6.n <- length(num5a)
num6.sd <- sd(num5a)
num6.se <- num6.sd/sqrt(num6.n)
num6.se
```


**b. Interpret the result.**

*This is how I get the state income means by dividing the sd() to sqrt() or length() and that is how I get the standard errors of the state income means and this was the result.*


***7. Use the titanic dataset.***

```{r,}
data(Titanic)
Titanic <- data.frame(Titanic)
```


**a. subset the titatic dataset of those who survived and not survived. Show the codes and its result.**

**Survived**
```{r,}
survive <- subset(Titanic, Survived == "Yes")
survive
```

**Not Survived**
```{r,}
died <- subset(Titanic, Survived == "No")
died
```


***8. The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases. The database therefore reflects this chronological grouping of the data. You can create this dataset in Microsoft Excel.***

**a. describe what is the dataset all about.**

**Answer =
*The data sets are about the breast cancer Wisconsin. The samples arrive periodically as Dr. Wolberg reports his clinical cases. The database therefore reflects this chronological grouping of the data*

**b. Import the data from MS Excel. Copy the codes.**

```{r,}
library("readxl")
library(tinytex)
```

```{r,}
num8b <- read_excel("C:\\Users\\neil navaroo\\Documents\\Breast_Cancer.xlsx")
num8b
```

**c. Compute the descriptive statistics using different packages. Find the values of:**

**c.1 Standard error of the mean for clump thickness.**

```{r,}
num8c1.n <- length(num8b$`CL. thickness`)
num8c1.sd <- sd(num8b$`CL. thickness`)
num8c1.se <- num8c1.sd/sqrt(num8b$`CL. thickness`)
num8c1.se
```


**c.2 Coefficient of variability for Marginal Adhesion.**

```{r,}
sd(num8b$`Marg. Adhesion`) / mean(num8b$`Marg. Adhesion`) * 100
```


**c.3 Number of null values of Bare Nuclei.**

```{r,}
num8c3 <- subset(num8b,`Bare. Nuclei` == "NA")
num8c3
```


**c.4 Mean and standard deviation for Bland Chromatin**

```{r,}
mean(num8b$`Bl. Cromatin`)
sd(num8b$`Bl. Cromatin`)
```


**c.5 Confidence interval of the mean for Uniformity of Cell Shape**

*Calculate the mean*

```{r,}
num8c5 <- mean(num8b$`Cell Shape`)
num8c5
```

*Calculate the standard error of the mean*

```{r,}
numA <- length(num8b$`Cell Shape`)
numB <- sd(num8b$`Cell Shape`)
numC <- numB/sqrt(numA)
numC
```

*Find the t-score that corresponds to the confidence level*

```{r,}
numD = 0.05
numE = numA - 1
numF = qt(p=numD/2, df=numE,lower.tail=F)
numF
```

*Constructing the confidence interval*

```{r,}
numG <- numF * numC
```

*Lower*

```{r,}
numH <- num8c5 - numG
```

*Upper*

```{r,}
numI <- num8c5 + numG
```

*Upper and Lower*

```{r,}
c(numH,numI)
```


**d. How many attributes?**

```{r,}
attributes(num8b)
```

*There are 3 and these are the class(3), row.name(49) and col.name/length(11).*

**e. Find the percentage of respondents who are malignant. Interpret the results.**

```{r,}
num8e <- subset(num8b, Class == "malignant")
num8e
```

*There 17 respondents who are malignant.*
*And there are total of 49 respondent.*

*Getting the percentage*

```{r,}
18  / 49 * 100
```

**There are 36.73469 or 37% of respondents who are malignant.**


***9. Export the data abalone to the Microsoft excel file. Copy the codes.***

```{r,}
library("AppliedPredictiveModeling")

data(abalone)
summary(abalone)
head(abalone)
```

**Exporting the data abalone to the Microsoft excel file**

```{r,}
library(xlsx)
write.xlsx("abalone","C:\\Users\\neil navaroo\\Documents\\abalone.xlsx")
```

