---
title: "Individual Project 2"
author: "Neil Francis N. Navarro"
date: "`r Sys.Date()`"
output: html_document
---

***Packages that will be needed***

```{r,}
library("twitteR") 
library(dplyr)
library(tidyr)
library("plotly")
library(ggplot2)
library(RColorBrewer)
library(tidytext)
library(rtweet)
library(tm)
library(slam)
library(wordcloud)
library(wordcloud2)
library(corpus)
```


***Extract from twitter using your developer's credentials. Choose any keyword you want.***

**Set-up credentials**

```{r, credentials}
CONSUMER_SECRET <- "41PDexRe92yfNTbt8a2fvJun8f90q9Zwz29uOGY7ZGhhag9CjK"
CONSUMER_KEY <- "UPrRGJE4UWIUnTxkEjTKHppF0"
ACCESS_SECRET <- "fcaPBNu4qYlU4q1UKXQQL3s8DKBEFnewwr38PGBJ2hlQp"
ACCESS_TOKEN <- "1595950464826507264-3WI3S7lwlHPgsMVpNzaGRVpjdWsUrn"
```


**connect to twitter app**

```{r,}
setup_twitter_oauth(consumer_key = CONSUMER_KEY,
                    consumer_secret = CONSUMER_SECRET,
                    access_token = ACCESS_TOKEN,
                    access_secret = ACCESS_SECRET)
```

***Extract 10000 tweets from Twitter using twitteR package including retweets.***

**Getting a data**

```{r,}
trendTweets2 <- searchTwitter("#tiktok",
                             n = 10000,
                             lang = "en",
                             since = "2022-11-29",
                             until = "2022-12-03",
                             retryOnRateLimit=120)

trendTweets2
```

***Subset the retweets and the original tweets into a separate file***

**Converting data into dataframe**
```{r,}
trendTweetsDF2 <- twListToDF(trendTweets2)

save(trendTweetsDF2,file = "trendingTweetsDF2.Rdata")
```


***Original Tweets***

**Subsetting using the dplyr()package**

```{r,}
original <- trendTweetsDF2 %>%
  select(screenName,text,created,statusSource,isRetweet) %>% 
  filter(isRetweet == "FALSE")

save(original, file = "original.Rdata")
```

**GROUPING THE DATA CREATED** 

```{r,}
original %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))
```

```{r,}
originals <- original %>%  mutate(Created_At_Round = created %>% round(units = 'hours') %>% as.POSIXct())
originals
```

```{r,}
mn <- original %>% pull(created) %>% min()
mn 
mx <- original %>% pull(created) %>% max()
mx
```


***Retweets***
**Subsetting using the dplyr()package**

```{r,}
retweet <- trendTweetsDF2 %>%
  select(screenName,text,created,statusSource,isRetweet) %>% 
  filter(isRetweet == "TRUE")

save(retweet, file = "retweet.Rdata")
```

**GROUPING THE DATA CREATED**

```{r,}
retweet %>%  
  group_by(1) %>%  
  summarise(max = max(created), min = min(created))
```

```{r,}
retweets <- retweet %>%  mutate(Created_At_Round = created %>% round(units = 'hours') %>% as.POSIXct())
retweets
```

```{r,}
min1 <- retweet %>% pull(created) %>% min()
min1 
max1 <- retweet %>% pull(created) %>% max()
max1
```

***Plot the retweets and the original tweets using bar graph in vertical manner. With legends.***

***Original tweets***

```{r,}
orig <- ggplot(originals, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "midnightblue", high = "purple")

orig %>% ggplotly()
```


***Retweets***

```{r,}
retwt <- ggplot(retweets, aes(x = Created_At_Round)) +
  geom_histogram(aes(fill = ..count..)) +
  theme(legend.position = "right") +
  xlab("Time") + ylab("Number of tweets") + 
  scale_fill_gradient(low = "yellowgreen", high = "aquamarine4")

retwt %>% ggplotly()
```
