---
title: "Work Sheet 3B"
author: "Neil Francis N. Navarro"
date: "2022-11-11"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

***Worksheet-3b in R***

*Instructions:*

**Use RStudio or the RStudio Cloud accomplish this worksheet.**

*Save the R script as RWorksheet_lastname 3b.R.*

*On your own GitHub repository, push the R script, the Rmd file, as well as this*
*pdf worksheet to the repo you have created before.*

*Do not forget to comment your Git repo on our VLE*

*Accomplish this worksheet by answering the questions being asked and writing*
*the code manually.*

install.packages("dplyr")
library(dplyr)
library(tidyverse)


***1. Create a data frame using the table below.***
 
**a.Write the codes.**
 
```{r, 1A}
Respondents <- c(seq(1,20))
Sex <- c(2,2,1,2,2,2,2,2,2,2,1,2,2,2,2,2,2,2,1,2)
FathersOccupation <- c(1,3,3,3,1,2,3,1,1,1,3,2,1,3,3,1,3,1,2,1)
Personsathome <- c(5,7,3,8,5,9,6,7,8,4,7,5,4,7,8,8,3,11,7,6) 
Siblingsatschool <- c(6,4,4,1,2,1,5,3,1,2,3,2,5,5,2,1,2,5,3,2)
Typesofhouses <- c(1,2,3,1,1,3,3,1,2,3,2,3,2,2,3,3,3,3,3,2)
data_frame <- data.frame(Respondents,Sex,FathersOccupation,Personsathome,
Siblingsatschool,Typesofhouses)
```

**b.Describe the data. Get the structure or the summary of the data**

```{r, 1B}
summary(data_frame)
```

**c. Is the mean number of siblings attending is 5?**

"Answer: No"

**d. Extract the 1st two rows and then all the columns using the subsetting functions.**
**Write the codes and its output.**

```{r, 1C}
c1 <- subset(data_frame[1:2, 1:6, drop = FALSE])
c1
```

**e. Extract 3rd and 5th row with 2nd and 4th column. Write the codes and its result.**
 
```{r, 1E}
c2 <- subset(data_frame[c(3,5),c(2,4)])
c2
```

**f. Select the variable types of houses then store the vector that results as types_houses.**
**Write the codes.**
 
```{r, 1F}
c3 <- data_frame[c(6)]

type_houses <- c3
```

**g. Select only all Males respondent that their father occupation was farmer. Write**
**the codes and its output.**
 
```{r, 1G}
c22 <- subset(data_frame[c(3,11),c(2,3)])
c22
```




**h. Select only all females respondent that have greater than or equal to 5 number**
**of siblings attending school. Write the codes and its outputs**

```{r, 1H}
c5 <- subset(data_frame[c(1:20), c(2,5)])
girl <- c5[data_frame$Siblingsatschool >= 5,]
girl
```

 ***2. Write a R program to create an empty data frame. Using the following codes:***
 
```{r, 2a}
  dtframe = data.frame(Ints=integer(),
                  Doubles=double(), Characters=character(),
                  Logicals=logical(),
                  Factors=factor(),
                  stringsAsFactors=FALSE)
print("Structure of the empty dataframe:")
print(str(dtframe))
```
